How "..." Behaves in R
======

# So what does `...` mean anyway?

The R documentation has precious little to say about the `...`
construct. Here I'll try to show how what it does, how it works, and
how the `fexpr` package enhances your ability to do things with it.

### What `...` means in a function header?

Here is an example function definition:

```{r}
function(x, y, ...) {
  with(x, doTheThing(y, ...))
}
```

The function header declares three arguments: `x`, `y`, and
`...`. Of these, `...` is treated specially.

Whenever a function call is made, the R interpreter matches up the
argument list and against the defined arguments of a function. If the
argument list in the header contains `...`, any arguments that don't
match the other named arguments get bundled up in `...`. Otherwise,
non-matching arguments cause an error.

There are equivalent mechanisms in other languages. For example in
Python, our function might be specified as follows:

```{python, exec=FALSE}
def myFun(x, y, *args, **kwargs):
    with(x, doTheThing(y, *args), **kwargs)
```

Here `*args` and `**kwargs` are playing the role that `...` plays in
R. Any named arguments that don't match get put into the dict
`kwargs`; excess unnamed arguments get put into the list `args`.
One difference is that Python keeps "named" and "unnamed" 
arguments separate while R mixes both kinds into `...`

### What does `...` mean in function code?

If `...` appears in the list of arguments to call a function, it is
treated specially by the interpreter. The arguments saved in `...` are unpacked,
and those arguments are pasted into the argument list for the function.

```
```

Note that `list` does not know that its arguments came out of a `...`.

This behavior is a lot like "argument interpolation" in Python, where
you use the 

### Where do the arguments named `...` live?

In a variable local to the function, named `...`!

```{r}
function(x, y, ...) {

}
```

Note that `...` is not bound to any value when it is empty. The R
interpreter checks this condition and

Because `...` is a reserved word, just writing `...` in code will not
show you the value of that variable. but you can (in current R) access
it using `get()`.

EXAMPLE

### What kind value is bound to `...`?

What goes in `...` is a special type of object, in the R souece it is
called a DOTSXP. Which is very similar to a "pairlist," except that it
has a different type. Further Each element of the `DOTSXP` is a
*promise* (called PROMSXP in the R code).

R always expects a `DOTSXP` to be assigned to the `...` name. Any
other type will cause an error. There is no user-level interface to
create a DOTSXP (but the point of `fexpr` is to provide such functions.)

A *promise* is what is created for each argument that is passed to a
function, and supports R's lazy evaluation of function arguments. A
promise consists of three parts: an expression, an environment to
evaluate it in, and the value (after it has been evaluated)

In this case, we see from 'substitute' that the original expressions
are preserved through the

### Relation between `...` and lazy evaluation

Every element in `...` is a promise (with its , and each argument to a
function becomes a promise

This has a very important consequence; it means that the environment
of your argument might *not* be that of your caller, if your caller
used `...` to hand down arguments. For this reason, the common pattern
of using `parent.frame` or `match.call` in conjunction with `eval` to
perform non-standard evaluation is fragile; for the correct
patterns see the vignette `XXX`.

### How arguments get put into `...`

M-
