Wrapping Nonstandard-evaluating functions
=====

##### Or, how to use Metaprogramming to work around other people's code that used Metaprogramming

## Automating graph labels.

Probably the most frequent and mundane application of non-standard evaluation is to
automate writing axis labels. Here is code that plots a sine curve:

```{r}
x <- seq(0, 2 * pi, length = 100)
plot(x, sin(x), type = "l")
```

The graph that is produced has labels on its horizontal axis,  `sin(x)` and `x` 
on the vertical axis.

If, instead, we stored `sin(x)` in a variable `y`, a different label is drawn on the Y axis.
```{r}
y <- sin(x)
plot(x, y, type = "l")
```

So plotting `y <- sin(x)` does not mean that wrting `y` is equivalent to writing `sin(x)`. `plot` is still able to tell the difference.

In *standard evaluation* a function only depends on the value of its arguments. If `y` is defined to have the value of `sin(x)`, then `f(y)` should do the same thing as `f(sin(x))`. Clearly `plot` breaks this rule. The R community has calls this `non-standard evaluation`. A function that uses non-standard evalution can have behavtior depends on the way its argument is written, not just what values they evaluate to.

### NSE makes it difficult to wrap functions.

Let's say we wanted to make a function `lineplot` that behaves just like `plot` but has a default plot argument.

I want to make that a hard rule. Writing `lineplot(x, sin(y))` should function _exactly_ as writing `plot(x, sin(y), sin(x))

```
lineplot <- function(x, y, type="l", ...) {
  plot(x, y, type, ...)
}

lineplot(x, sin(x))
```

But our axis label is now wrong. It now always says `x` and `y` instead of `sin(y)` or whatever else we might have wrote. `lineplot` didn't live up to the spec of behaving just like `plot` but for one detail.

### The NSE package easily wraps NSE functions with `invoke`

It's harder to fix this problem than you might think, so I'll first show `nse`'s way of writing `lineplot`:

```{r}
lineplot <- function(x, y, type="l", ...) {
  invoke(plot)(x, y, type=type, ...)
}

lineplot(x, sin(x))
```

Here's how it works. `invoke(plot)` returns a function. That function takes its arguments by name instead of evaluating them. 

### R's builtin facilities have weird edge cases

Here are various ways base R provides of writing `lineplot` that all don't quite meet the spec.

```

```

Counterargument:
do(plot(x=x, y=y)

### How to wrap "plot"

### How to wrap an NSE function in a higher order function

### match.call vs. default arguments

### match.call vs. ...

### parent.frame() vs. default arguments.

### pass data to an indirect function, without blowing up the stacktrace

# EXAMPLE

Using `arg_env` instead of `parent_frame` also allows non-standard-evaluating
functions to be composable. (example with dlply and glm functions)

## caller and with_caller

In writing NSE functions you should as much as possible use `arg_env`
to determine where arguments come from. First convert all uses of
`parent.frame()` into `arg_env()`.  Where a function is called from is
another thing, called `caller()`. This is actually a bit different
from what `parent.frame()` does. `caller()` guards against giving
surprising (wrong) results in situations involving lazy evaluation or
when the caller can no longer be determined -- it prefers to throw
errors instead.

Here is a practical example of why.



## Argument lists and `...`

In R, to write a function that takes any number of arguments, we use
the symbol `...`, which represents a sort of list of arguments. This
is somewhat similar to Python's solution of `*args, **kwargs`, except
that while in Python variadic arguments are stored in first-class data
structures, in R the `...` is opaque. It's tricky to do things like
take the second argument, or take all the odd arguments, or obtain a
list of argument names without forcing them, or concatenating two
argument lists together. The only thing you can do with a `...` when
you have it is to pass them all to another function's argument list.

But under the hood, a `...` is just a named list of promises. The
`nse` package provides a `dots` class and accessor functions that
let you manipulate sequences of promises the same way as you would
manipulate other kinds of lists.

As an example, consider trying to implement the R library function
`switch`. This takes any number of arguments, and uses the argument
`expr` -- either a number or a name -- to decide which of the other
arguments to return, only forcing that argument. But in base R it is
difficult to access unevaluated arguments by index or name, so
`switch` has a C implementation.

It's actually possible to implement `switch` in base R, but... coming
up with a solution requires a bit of tinkering. I can do it by
synthesizing a function with the right arglist to match the required
argument. The weirdest part was working out how names like `..3` work.

```r
switch2 <- function(expr, ...) {
  n <- names(substitute(list(...)))[-1]
  if (!is.null(n))
      arglist <- as.pairlist(structure(
          rep(list(quote(expr=)), length(n)),
          names=n))
  else
      (arglist <- as.pairlist(alist(...=)))

  if (is.numeric(expr))
      body <- as.name(paste0("..", expr))
  else
      body <- as.name(expr)
  f <- eval(substitute(`function`(arglist, body),
                         list(arglist=arglist, body=body)))
  f(...)
}
```

The point of this digression is that with a direct interface to
manipulate argument lists, `switch` is easy:

```{r}
switch3 <- function(expr, ...) {
  force_(dots(...)[[expr]])
}
```

## Missing arguments.

When a function defined as having an argument but that argument is not
given, that argument is "missing."

For example,

```r
f <- function(x) missing(x)
f(1) ##FALSE
f() ## X
```
